---
title: "National Health Survey"
author: "Ronae McLin"
date: "11/16/2020"
output: github_document
---

## importing and tidying the National Health Survey data 

***focus is on flu vaccines***

```{r}
library(tidyverse)
```

not really sure what this data set contains. need to look into this more
```{r}
person_df = 
  read_csv("personsx.csv")
```


adult sample for 2019

** there is ALOT of information and variables within this dataset.  we can take this into many different directions **
```{r}
  adult_df = 
  read_csv("adult19.csv")
```


- was SA pregnant last flu season?
- flu vaccine
- month of last flu vaccine,
- year of last flu vaccine
- was flu shot before or during pregnancy?
- earlier pregnancy and flu vaccine
- etc....

there is an interesting category pertaining to mobility, this could be helpful if we end up discussing accessbility to loaction to obtain a flu shot

there is also interesting category of variables pertaining to insurance plans and coverage.

interesting category of variables pertaining to utilization of healthcare services, outside of the scope of only flu vaccines. 
```{r}
flu_adult_df =
  adult_df %>% 
  janitor::clean_names() %>% 
  select(
    srvy_yr,agep_a, age65, sex_a, educ_a,hisp_a, hispallp_a, hisdetp_a, raceallp_a,phstat_a,bmicat_a, notcov_a, cover_a, cover65_a, usualpl_a, usplkind_a,  pregfluyr_a, shtflu12m_a, shtflum_a, shtfluy_a, flupreg_a, flupreg2_a
  )


```

